---
title: "Data607 Week1 Approach"
date: "01-29-2026"
name: "Daivd Chen"
format: html
editor: visual
---

```{r}
library(ggplot2)
library(tidyverse)

```

## Introducation

This dataset comes from NYC Open Data and is publicly available. I selected it to analyze real estate market trends, including new building developments and property flips. The entire dataset in CSV format is over 554 MB, so I may need to trim down the size for easier processing.

https://data.cityofnewyork.us/d/rbx6-tga4


https://raw.githubusercontent.com/dyc-sps/SPS-Data607-Week1/refs/heads/main/DOB_NOW__Build_%E2%80%93_Approved_Permits_20260129_QUEENS_AFTER_2025.csv


(updated dataset link)
https://raw.githubusercontent.com/dyc-sps/SPS-Data607-Week1/refs/heads/main/DOB_NOW__Build_Elevator_Permit_Applications_20260201_from_20240201.csv
### Approach

The second reason was to identify which elevator companies in our area have submitted the most permits, which may relate to their reputation. The elevator company serving our building has been unreliable. They frequently fail to arrive on time and often charge overtime rates simply because they show up after normal business hours. Therefore, we have replaced three companies in the past two years and are now looking for another one. We are trying to use public data to find a more suitable company for our building. 
The biggest challenge is determining how the data can indicate which company is better or meets our specific requirements.


### 

```{r}
mydata <- read.csv("https://raw.githubusercontent.com/dyc-sps/SPS-Data607-Week1/refs/heads/main/DOB_NOW__Build_Elevator_Permit_Applications_20260201_from_20240201.csv", header = TRUE)
```
```{r}
names(mydata)
```
```{r}
new_data <- mydata %>%
  filter(Filing.Status == "Signed Off") %>%
  group_by(Applicant.License.Number) %>%
  summarise(n=n())
```

```{r}
ggplot(new_data, aes(x = Applicant.License.Number, y=n, color=n, size = n))+
         geom_point()
       
```



### LLMS used:


•	OpenAI. (2025). ChatGPT (Version 5.2) [Large language model]. https://chat.openai.com. Accessed Feb 1, 2026.


